%%%%%%%%%%%%%%%%%%%%%%
\documentclass{singlecol-new}
%%%%%%%%%%%%%%%%%%%%%%

\usepackage{natbib,stfloats}
\usepackage{mathrsfs,amsmath,upgreek}
\usepackage{graphicx}

\def\newblock{\hskip .11em plus .33em minus .07em}

\newcommand{\be}{\begin{eqnarray}}
\newcommand{\ee}{\end{eqnarray}}
\newcommand{\nn}{\nonumber}

\theoremstyle{TH}{
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corrolary}[lemma]{Corrolary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{stheorem}[lemma]{Wrong Theorem}
\newtheorem{algorithm}{Algorithm}
}

\theoremstyle{THrm}{
\newtheorem{definition}{Definition}
\newtheorem{question}{Question}
\newtheorem{remark}{Remark}
\newtheorem{scheme}{Scheme}
}

\theoremstyle{THhit}{
\newtheorem{case}{Case}[section]
}

\makeatletter

\def\Reals{\mathbb{R}}
\def\Ints{\mathbb{Z}}
\def\Nats{\mathbb{N}}

\def\theequation{\arabic{equation}}

\def\tc{\textcolor{red}}

\def\BottomCatch{%
\vskip -10pt
\thispagestyle{empty}%
\begin{table}[b]%
\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
\\[-12pt]
Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
\end{tabular*}%
\vskip -30pt%
%%\vskip -35pt%
\end{table}%
%\def\tc{\textcolor}{red}
} \makeatother

%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%

\thispagestyle{plain}

\setcounter{page}{1}

\LRH{xxxx}

\RRH{xxxx}

\VOL{x}

\ISSUE{x}

\PUBYEAR{xxxx}

%\BottomCatch

%\CLline

%\subtitle{}

\title{Elastic Hadoop Cluster in a Scaled-out Object Store}
%\title{Adding Data Analytics Capabilities to a Scaled-out Storage Cluster}

\authorA{xxxx}

\affA{xxxx*\\
*Corresponding author}

\authorB{xxxx}
\affB{xxxx}

\begin{abstract}
\label{sec-abstract}
\input{sections/abstract}
\end{abstract}

\KEYWORD{xxxx}

\REF{to this paper should be made as follows: xxxx (xxxx) `xxxx',
{\it xxxx}, Vol.~x, No.~x, pp.xxx--xxx.}

\begin{bio}
\tc{AUTHOR PLEASE SUPPLY CAREER HISTORY OF NO MORE THAN 100 WORDS
FOR EACH AUTHOR.}
\end{bio}

\maketitle

\section{Introduction}
\label{sec-introduction}
\input{sections/introduction}

\section{Background}
\input{sections/background}

\section{Proposed Method Architecture}
\input{sections/proposedmethod}

\section{Performance Evaluation}
\label{sec-performance}
\input{sections/evaluations}

\section{Related Work}
\label{sec-related}
\input{sections/relatedwork}

\section{Conclusions}
\input{sections/conclusion}
\label{sec-conclusion}

\section*{Acknowledgements}



\begin{thebibliography}{99}

%\bibitem[\protect\citeauthoryear{xxxx}{2011}]{Zhang11}
%xxxx (2011) `Reliable packets delivery over segment-based multi-path
%in wireless ad hoc networks', {\it Pervasive Computing and
%Applications (ICPCA), 2011 6th International Conference on},
%pp.300-–306. \tc{AUTHOR PLEASE SUPPLY LOCATION.}

\bibitem[\protect\citeauthoryear{(Amazon Elastic Compute Cloud,
http://aws.amazon.com/ec2/)}{}]{amazon_ec2}
Amazon Elastic Compute Cloud, http://aws.amazon.com/ec2/

\bibitem[\protect\citeauthoryear{(Amazon Simple Storage Service,
http://aws.amazon.com/s3/)}{}]{amazon_s3}
Amazon Simple Storage Service, http://aws.amazon.com/s3/

\bibitem[\protect\citeauthoryear{(Hadoop Cluster Setup,
http://hadoop.apache.org/docs/r1.2.1/cluster\_setup.html)}{}]{hadoopconf}
Hadoop Cluster Setup, http://hadoop.apache.org/docs/r1.2.1/cluster\_setup.html

\bibitem[\protect\citeauthoryear{(Hadoop JIRA HDFS-941,
https://issues.apache.org/jira/browse/HDFS-941)}{}]{hdfs941}
Hadoop JIRA HDFS-941, https://issues.apache.org/jira/browse/HDFS-941

\bibitem[\protect\citeauthoryear{(Google Compute Engine,
https://cloud.google.com/compute/)}{}]{gce}
Google Cloud Platform - Compute Engine, https://cloud.google.com/compute/

\bibitem[\protect\citeauthoryear{(Wilson et al., 2014)}{}]{wilsonhadoop}
Wilson, E. H., Kandemir, M. T. and Gibson, G. (2014)
'Will they blend?: Exploring big data computation atop traditional hpc nas storage',
{\it IEEE 34th International Conference on Distributed Computing Systems (ICDCS)},
pp.524--534

\bibitem[\protect\citeauthoryear{(Ali et al., 2008)}{}]{revisitmd}
Ali, N., Devulapalli, A., Dalessandro, D., Wyckoff, P. and Sadayappan, P. (2008)
'Revisiting the metadata architecture of parallel file systems',
{\it IEEE Petascale Data Storage Workshop (PDSW)},
pp.1--9

\bibitem[\protect\citeauthoryear{(Xu et al., 2015)}{}]{hadooplustre}
Xu, C., Goldstone, R., Liu, Z., Chen, H., Neitzel, B. and Yu, W. (2015)
'Exploiting Analytics Shipping with Virtualized MapReduce on HPC Backend Storage Servers',
{\it IEEE Transactions on Parallel and Distributed Systems},
Vol. PP, No. 99, p. 1

\bibitem[\protect\citeauthoryear{(Rutman, 2011)}{}]{rutman}
Rutman, N. (2011)
'Map/reduce on lustre, white paper',
{\it Technical report, Xyratex Technology Limited},
Havant, Hampshire, UK.

\bibitem[\protect\citeauthoryear{(Yu and Kulkarni, 2014)}{}]{hadoopyarnprogress}
Yu, W. and Kulkarni, O. (2014)
'Progress Report on Efficient Integration of Lustre and Hadoop/YARN',
{\it The Lustre User Group Conference},
Miami, FL, USA.

\bibitem[\protect\citeauthoryear{(Kathpal and Yasa, 2014)}{}]{nakshatra}
Kathpal, A. and Yasa, G. A. N. (2014)
'Nakshatra: Towards running batch analytics on an archive',
{\it IEEE 22nd International Symposium on Modelling, Analysis \&
Simulation of Computer and Telecommunication Systems (MASCOTS)},
pp.479--482

\bibitem[\protect\citeauthoryear{(Palanisamy et al., 2014)}{}]{vncache}
Palanisamy, B., Singh, A., Mandagere, N., Alatorre, G. and Liu, L. (2014)
'Mapreduce analysis for cloud-archived data',
{\it 14th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing (CCGrid)},
pp.51--60

\bibitem[\protect\citeauthoryear{(Sevilla et al., 2014)}{}]{supmr}
Sevilla, M., Nassi, I., Ioannidou, K., Brandt, S. and Maltzahn, C. (2014)
'SupMR: Circumventing Disk and Memory Bandwidth Bottlenecks for Scale-up MapReduce',
{\it IEEE Parallel and Distributed Processing Symposium Workshops (IPDPSW)},
pp.1505--1514

\bibitem[\protect\citeauthoryear{(Cheng et al., 2015)}{}]{chengcast}
Cheng, Y., Iqbal, M. S., Gupta, A and Butt, A.R. (2015)
'CAST: Tiering Storage for Data Analytics in the Cloud',
{\it ACM 24th International Symposium on High-Performance Parallel and
Distributed Computing (HPDC)},
New York, NY, USA.
pp.45--56

\bibitem[\protect\citeauthoryear{(Rupprecht et al., 2014)}{}]{rupprechtbd}
Rupprecht, L., Zhang, R. and Hildebrand, D. (2014)
'Big Data Analytics on Object Stores: A Performance Study',
{\it SuperComputing (SC)},
New Orleans, LA, USA.

\bibitem[\protect\citeauthoryear{(Using Lustre with Apached Hadoop,
http://wiki.lustre.org/images/1/1b/Hadoop\_wp\_v0.4.2.pdf)}{}]{lustre_with_hadoop}
Using Lustre with Apache Hadoop,
http://wiki.lustre.org/images/1/1b/Hadoop\_wp\_v0.4.2.pdf

\bibitem[\protect\citeauthoryear{(Dean and Ghemaway, 2008)}{}]{Dean:2008:MSD:1327452.1327492}
Dean, J. and Ghemawat, S. (2008) 'MapReduce: Simplified Data Processing
on Large Clusters', {\it Communications of the ACM - 50th Anniversary Issue},
Vol. 51, No. 1, pp.107--113

\bibitem[\protect\citeauthoryear{(Sathiamoorthy et al., 2013)}{}]{Sathiamoorthy:2013:XEN:2488335.2488339}
Sathiamoorthy, M., Asteris, M., Papailiopoulos, D., Dimakis, A. G., Vadali, R., Chen, S. and Borthakur, D. (2013)
'Xoring elephants: Novel erasure codes for big data',
{\it VLDB Endowment},
Vol. 6, No. 5, pp.325--336

\bibitem[\protect\citeauthoryear{(Cheng et al., 2012)}{}]{conf/cluster/ChengLMXQRZG12}
Cheng, Z., Luan, Z., Meng, Y., Xu, Y., Qian, D., Roy, A., Zhang, N. and Guan, G. (2012)
'Erms: an elastic replication management system for hdfs',
{\it IEEE International Conference on Cluster Computing Workshops (CLUSTER WORKSHOPS)}
pp.32--40

\bibitem[\protect\citeauthoryear{(Fan et al., 2011)}{}]{Fan11diskreduce:replication}
Fan, B., Tantisiriroj, W., Xiao, L. and Gibson, G. (2011)
'Diskreduce: Replication as a prelude to erasure coding in data-intensive scalable computing'
Parallel Data Laboratory, Carnegie Mellon University, Pittsburgh, PA, USA.

\bibitem[\protect\citeauthoryear{(Ananthanarayanan et al., 2009)}{}]{Ananthanarayanan:2009:CAW:1855533.1855548}
Ananthanarayanan, R., Gupta, K., Pandey, P., Pucha, H., Sarkar, P., Shah, M. and Tewari, R. (2009)
'Cloud analytics: Do we really need to reinvent the storage stack',
{\it 1st USENIX Workshop on Hot Topics in Cloud Computing (HOTCLOUD)},
San Diego, CA, USA.

\bibitem[\protect\citeauthoryear{(Tantisiriroj et al., 2011)}{}]{Tantisiriroj:2011:DDF:2063384.2063474}
Tantisiriroj, W., Son, S. W., Patil, S., Lang, S. J., Gibson, G. and Ross, R. B. (2011)
'On the duality of data-intensive file system design: reconciling HDFS and PVFS',
{\it ACM 2011 International Conference for High Performance Computing, Networking, Storage and Analysis},
p. 67

\bibitem[\protect\citeauthoryear{(Wang et al., 2009)}{}]{Wang:2009:KHG:1645164.1645176}
Wang, J., Crawl, D. and Altintas, I. (2009)
'Kepler+ Hadoop: a general architecture facilitating data-intensive applications in scientific workflow systems',
{\it ACM 4th Workshop on Workflows in Support of Large-Scale Science},
p. 12

\bibitem[\protect\citeauthoryear{(Xu et al., 2010)}{}]{Xu:2010:IHP:1807167.1807272}
Xu, Y., Kostamaa, P. and Gao, L. (2010)
'Integrating hadoop and parallel DBMs',
{\it ACM SIGMOD International Conference on Management of data},
pp.969--974

\bibitem[\protect\citeauthoryear{(Ibrahim et al., 2012)}{}]{6217451}
Ibrahim, S., Jin, H., Lu, L., He, B., Antoniu, G. and Wu, S. (2012)
'Maestro: Replica-aware map scheduling for mapreduce',
{\it 12th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing (CCGrid)}
pp.435--442

\bibitem[\protect\citeauthoryear{(Eltabakh et al., 2011)}{}]{Eltabakh:2011:CFD:2002938.2002943}
Eltabakh, M. Y., Tian, Y., Özcan, F., Gemulla, R., Krettek, A. and McPherson, J. (2011)
'CoHadoop: flexible data placement and its exploitation in Hadoop',
{\it VLDB Endowment},
Vol. 4, No. 9, pp.575--585.

\bibitem[\protect\citeauthoryear{(Porter, 2010)}{}]{Porter:2010:DSC:1773912.1773923}
Porter, G. (2010)
'Decoupling storage and computation in hadoop with superdatanodes'
{\it ACM SIGOPS Operating Systems Review}
Vol. 44, No. 2, pp.41--46.

\bibitem[\protect\citeauthoryear{(Ananthanarayanan et al., 2011)}{}]{Ananthanarayanan:2011:SCS:1966445.1966472}
Ananthanarayanan, G., Agarwal, S., Kandula, S., Greenberg, A., Stoica, I., Harlan, D. and Harris, E. (2011)
'Scarlett: coping with skewed content popularity in mapreduce clusters',
{\it ACM 6th Conference on Computer Systems},
pp.287--300

\bibitem[\protect\citeauthoryear{(Mihailescu et al., 2013)}{}]{180733}
Mihailescu, M., Soundararajan, G. and Amza C. (2013)
'MixApart: Decoupled Analytics for Shared Storage Systems',
{\it 11th USENIX Conference on File and Storage Technologies},
pp.133--146

\bibitem[\protect\citeauthoryear{(Gantz and Reinsel, 2012)}{}]{idcbigdata}
Gantz, J. and Reinsel, D. (2012) 'The digital universe in 2020: Big data,
bigger digital shadows, and biggest growth in the far east', {\it
IDC iView: IDC Analyze the Future 2007}, pp.1--16

\bibitem[\protect\citeauthoryear{(Lustre,
http://wiki.lustre.org/index.php/Main\_Page)}{}]{lustre_web}
Lustre, http://wiki.lustre.org/index.php/Main\_Page

\bibitem[\protect\citeauthoryear{(Maltzahn et al., 2010)}{}]{maltzahn2010ceph}
Maltzahn, C., Molina-Estolano,  E., Khurana, A., Nelson, A.J., Brandt, S.A. and Weil, S. (2010)
'Ceph as a Scalable Alternative to the Hadoop Distributed File System',
{\it login: The USENIX Magazine},
Vol. 35, pp.38--49.

\bibitem[\protect\citeauthoryear{(Shvachko, 2010)}{}]{shvachko2010hdfs}
Shvachko, K.V. (2010)
'HDFS Scalability: The Limits to Growth',
{\it login:: the magazine of USENIX \& SAGE},
Vol. 35, No. 2, pp.6--16

\bibitem[\protect\citeauthoryear{(OpenStack Swift,
https://wiki.openstack.org/wiki/Swift)}{}]{openstack_swift}
OpenStack Swift, https://wiki.openstack.org/wiki/Swift

\bibitem[\protect\citeauthoryear{(Object-Based Storage Devices-3,
http://www.t10.org/)}{}]{osd3}
Object-Based Storage Devices-3, http://www.t10.org/

\bibitem[\protect\citeauthoryear{(Shvachko et al., 2010)}{}]{apache_hadoop}
Shvachko, K., Kuang, H., Radia, S. and Chansler, R. (2010)
'The Hadoop Distributed File System',
{\it IEEE 26th Symposium on Mass Storage Systems and Technologies (MSST)},
pp.1--10

\bibitem[\protect\citeauthoryear{(Weil et al., 2006)}{}]{cephorig}
Weil, S. A., Brandt, S. A., Miller, E. L., Long, D. D. and Maltzahn, C. (2006)
'Ceph: A scalable, high-performance distributed file system',
{\it USENIX 7th Symposium on Operating Systems Design and Implementation},
pp.307--320

\bibitem[\protect\citeauthoryear{(Carns et al., 2000)}{}]{Carns:2000:PPF:1268379.1268407}
Carns, P. H., Ligon, III, W. B., Ross, R. B. and Thakur, R. (2000)
'PVFS: A Parallel File System for Linux Clusters',
{\it 4th Annual Linux Showcase \& Conference (ALS'00)},
Vol. 4, p. 28

%\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
%Myneni, S. and  Patel, V.L. (2010) 'Organization of biomedical data
%for collaborative scientific research: a research information
%management system', {\it International Journal of Information
%Management}, Vol. 30, No. 3, pp.256--264
%
%\bibitem[\protect\citeauthoryear{Bekelman et al.}{2003}]{bekelman03}
%Bekelman, J.E., Li, Y. and Gross, C.P. (2003) 'Scope and impact of
%financial conflicts of interest in biomedical research: a systematic
%review', {\it JAMA}, Vol. 289, No. 19, pp.454--65
%
%\bibitem[\protect\citeauthoryear{Stein}{2008}]{stein08}
%Stein, L.D. {2008} 'Towards a cyberinfrastructure for the biological
%sciences: progress, visions and challenges', {\it Nature Reviews
%Genetics}, Vol. 9, No. 9, pp.678--688.
%
%\bibitem[\protect\citeauthoryear{NIH Statement on Sharing Scientific Research
%Data}{http://grants.nih.gov/grants/policy/data\_sharing/}]{nih03datasharing}
%NIH Statement on Sharing Scientific Research Data,
%http://grants.nih.gov/grants/policy/data\_sharing/
%
%\bibitem[\protect\citeauthoryear{Policy for sharing of data obtained in NIH supported or conducted
%genome-wide association studies}{2008}]{nih08policy} Policy for
%sharing of data obtained in NIH supported or conducted genome-wide
%association studies,
%http://grants.nih.gov/grants/guide/notice-files/not-od-07-088.html
%
%\bibitem[\protect\citeauthoryear{Network for Translational Research (NTR): Optical Imaging in
%Multimodality
%Platforms}{http://imaging.cancer.gov/programsandresources/speci\break
%alizedinitiatives/ntroi}]{ntr} Network for Translational Research
%(NTR): Optical Imaging in Multimodality Platforms,
%http://imaging.cancer.gov/programsandresources/specializedinitiatives/ntroi
%
%\bibitem[\protect\citeauthoryear{Piwowar~et~al.}{2008}]{piwowar08culture}
%Piwowar, H., Becich, M., Bilofsky, H. and Crowley, R. (2008) `PLoS
%medicine', {\it Sept, No. 9, Towards a Data Sharing Culture:
%Recommendations for Leadership from Academic Health Centers},
%Vol.~5.
%
%\bibitem[\protect\citeauthoryear{Birnholtz et al.}{2003}]{birnholtz03data}
%Birnholtz, J.P. and Bietz, M.J. (2003) `Data at work: supporting
%sharing in science and engineering', {\it GROUP}, pp.339--348.
%
%\bibitem[\protect\citeauthoryear{Data Sharing \& Intellectual Capital (DSIC) Workspace}
%{https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG}]{dsic} Data
%Sharing \& Intellectual Capital (DSIC) Workspace,
%https://cabig.nci.nih.gov/working\_groups/DSIC\_SLWG
%
%\bibitem[\protect\citeauthoryear{Getting Connected with
%caBIG}{https://cabig.nci.nih.gov/getting\_connected/}]{cabigconnected}
%Getting Connected with caBIG, https://cabig.nci.nih.gov/\break
%getting\_connected/
%
%\bibitem[\protect\citeauthoryear{Digital Imaging and Communications in Medicine
%(DICOM)}{http://medical.nema.org/}]{dicom} Digital Imaging and
%Communications in Medicine (DICOM), http://medical.nema.org/
%
%\bibitem[\protect\citeauthoryear{The Cancer Genome Atlas (TCGA) Data Portal}{http://cancergenome.nih.gov/dataportal}]{tcga}
%The Cancer Genome Atlas (TCGA) Data Portal,
%http://cancergenome.nih.gov/dataportal
%
%\bibitem[\protect\citeauthoryear{National Biomedical Imaging
%Archive}{https://cabig.nci.nih.gov/tools/NCIA}]{nbia} National
%Biomedical Imaging Archive, https://cabig.nci.nih.gov/tools/NCIA
%
%\bibitem[\protect\citeauthoryear{caBIG: cancer Biomedical Informatics Grid}{http://caBIG.nci.nih.gov/}]{cabig}
%caBIG: cancer Biomedical Informatics Grid, http://caBIG.nci.nih.gov/
%
%\bibitem[\protect\citeauthoryear{Biomedical Informatics Research Network}{
%http://www.nbirn.net/}]{birn}
%Biomedical Informatics Research Network, http://www.nbirn.net/
%
%\bibitem[\protect\citeauthoryear{Cyberinfrastructure for the Biological Sciences: Plant Science
%Cyberinfrastructure Collaborative
%(PSCIC)}{http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm}]{pscic}
%Cyberinfrastructure for the Biological Sciences: Plant Science
%Cyberinfrastructure Collaborative (PSCIC),
%http://www.nsf.gov/pubs/2006/nsf06594/nsf06594.htm
%
%\bibitem[\protect\citeauthoryear{MIRC}{http://mirc.rsna.org}]{mirc}
%MIRC, http://mirc.rsna.org
%
%\bibitem[\protect\citeauthoryear{Foster and
%Iamnitchi}{2003}]{foster03p2p2grid} Foster, I. and Iamnitchi, A.
%(2003) `On death, taxes, and the convergence of peer-to-peer and
%grid computing', {\it IPTPS'03}.
%
%\bibitem[\protect\citeauthoryear{Keidl et al.}{2002}]{keidl02metadata}
%Keidl, M., Kreutz, A., Kemper, A. and Kossmann, D. (2002) `A publish
%{\&} subscribe architecture for distributed metadata management',
%{\it ICDE}.
%
%\bibitem[\protect\citeauthoryear{Taylor and Ives}{2006}]{taylor06reconcile}
%Taylor, N.E. and Ives, Z.G. (2006) `Reconciling while tolerating
%disagreement in collaborative data sharing', {\it SIGMOD}.
%
%\bibitem[\protect\citeauthoryear{Rader and Wash}{2008}]{rader08tag}
%Rader, E.J. and Wash, R. (2008) {\it CSCW}, pp.239-248, Influences
%on tag choices in del.icio.us.
%
%\bibitem[\protect\citeauthoryear{Halevy et~al.}{2006}]{halevy06integration}
%Halevy, A., Rajaraman, A. and Ordille, J. (2006) {\it VLDB, Data
%integration: the teenage years},
%http://portal.acm.org/citation.cfm?id=1182635.1164130
%
%\bibitem[\protect\citeauthoryear{Doan and Halevy}{2005}]{doan05semantic}
%Doan, A. and Halevy, A.Y. (2005) Semantic Integration Research in
%the Database Community: A Brief Survey, {\it AI Magazine}, Vol. 26,
%No. 1, pp.83--94.
%
%\bibitem[\protect\citeauthoryear{Beynon-Davies et~al.}{1997}]{beynon97}
%Beynon-Davies, P., Bonde, L., McPhee, D. and Jones, C.B. (1997) `A
%collaborative schema integration system', {\it Comput. Supported
%Coop. Work}, Vol. 6, No. 1, Norwell, MA, USA, pp.1--18, issn =
%0925-9724.
%
%\bibitem[\protect\citeauthoryear{Wang and Vergara-Niedermayr}{2008}]{wang08com}
%Wang, F. and Vergara-Niedermayr, C. (2008) `Collaboratively Sharing
%Scientific Data', {\it CollaborateCom}, pp.805--823.
%
%\bibitem[\protect\citeauthoryear{Chin and Lansing}{2004}]{chin04context} Chin Jr., G. and Lansing,
%C.S. (2008) `Capturing and Supporting Contexts for Scientific Data
%Sharing via the Biological Sciences Collaboratory', {\it CSCW}, ISBN
%1-58113-810-5.
%
%\bibitem[\protect\citeauthoryear{W3C XML Query (XQuery)}{http://www.w3.org/XML/Query}]{xquery}
%W3C XML Query (XQuery), http://www.w3.org/XML/Query
%
%\bibitem[\protect\citeauthoryear{Wang et al.}{2009}]{wang09security}
%Wang, F., Hussels, P. and Liu, P. (2009) `Securely and flexibly
%sharing a biomedical data management system', {\it SPIE}.
%
%\bibitem[\protect\citeauthoryear{Marlow et al.}{2006}]{marlow06tag}
%Marlow, C., Naaman, M., Boyd, D. and Davis, M. (2006) `Position
%Paper, Tagging, Taxonomy, Flickr, Article, ToRead', {\it
%Collaborative Web Tagging Workshop}.
%
%\bibitem[\protect\citeauthoryear{NCI Enterprise Vocabulary Services (EVS)}{http://ncicb.nci.nih.gov/NCICB /infrastructure /cacore\_overview
%/vocabulary}]{ncievs} NCI Enterprise Vocabulary Services (EVS),
%http://ncicb.nci.nih.gov/NCICB /infrastructure /cacore\_overview
%/vocabulary
%
%\bibitem[\protect\citeauthoryear{NCI Enterprise Vocabulary Services (EVS)}{http://ncicb.nci.nih.gov/NCICB /infrastructure /cacore\_overview
%/vocabulary}]{ncithesaurus} NCI Enterprise Vocabulary Services
%(EVS), http://ncicb.nci.nih.gov/NCICB /infrastructure
%/cacore\_overview /vocabulary
%
%\bibitem[\protect\citeauthoryear{Bafoutsou and Mentzas}{2002}]{bafoutsou2002281}
%Bafoutsou, G. and Mentzas, G. (2002) `Review and functional
%classification of collaborative systems', {\it International Journal
%of Information Management}, Vol. 22, No. 4, pp.281--305.
%
%\bibitem[\protect\citeauthoryear{Bos et al.}{2007}]{zimmerman07taxonomy}
%Bos, N., Zimmerman, A., Olson, J., Yew, J., Yerkie, J. and Dahl, E.
%et al. (2007) `From shared databases to communities of practice: A
%taxonomy of collaboratories', {\it Journal of Computer-Mediated
%Communication},  Vol. 12, No. 2.
%
%\bibitem[\protect\citeauthoryear{Myneni and Patel}{2010}]{myneni10col}
%Myneni, S. and  Patel, V.L. (2010) `Organization of biomedical data
%for collaborative scientific research: A research information
%management system', {\it International Journal of Information
%Management}, Vol. 30, No. 3, June, pp.256--264.
%
%\bibitem[\protect\citeauthoryear{myGrid}{http://www.mygrid.org.uk/}]{misc{mygrid}}
%myGrid, http://www.mygrid.org.uk/
%
%\bibitem[\protect\citeauthoryear{Pike and Gahegan}{2007}]{pike07}
%Pike, W. and Gahegan, M. (2007) `Beyond ontologies: Toward situated
%representations of scientific knowledge', {\it International Journal
%of Human-Computer Studies}, Vol. 65, No. 7, pp.674--688.
\end{thebibliography}


\section*{Appendix}

%We have proposed the CSD scheme that makes use of multiple bridge
%nodes within the close neighbourhood of the source and insecure
%neighbours. These bridge nodes cooperatively help to deliver secret
%link key information from the source towards the insecure
%neighbours. In the delivery process, no secret information is
%disclosed to any node en route. These routers simply forward the
%encrypted data. Even the bridge nodes only get to know partial
%information about the secrets that they help to deliver.

\end{document}

%\def\notesname{Note}
%
%\theendnotes

%\section*{Query}
%
%\tc{AQ1: AUTHOR PLEASE CITE FIGURE 8 IN TEXT.}

\end{document}
